Bayes network classifiers for fMRI

### 2012-11-09 article/article.tex
spelling

\indent In this study we use the same StarPlus data, and use machine learning algorithms to decode the cognitive states of subjects when they are looking at Pictures or when they are looking at sentences. An interesting difference between many applications of machine learning, and this study is that most machine learning algorithms have the goal of achieving the maximum possible discrimination between conditions or classes. However, for fMRI studies it is important that the pattern of activity that is identified by the algorithm is a pattern associated with the cognitive state. When using non-linear classifiers, it is possible to decode features predictive of the cognitive state, where the brain does not actually respond to these features. For example, when decoding the primary visual cortex with high enough spatial resolution, it would be possible to combine simple features with a non-linear neural network to decode the presence or absence of, for example, faces. However, this information is not actually processed in that part of the brain \cite{to:2012rev}. To avoid this problem it is recommended to only use linear classifiers when decoding cognitive states from fMRI data. The classifiers that we compare in this paper are Gaussian Naive Bayesian (GNB) classifiers, Linear Support Vector (LSV) machines, and a Multivariate Gaussian (MV) classifier.

>>>>

\indent In this study we use the same StarPlus data from the previously mentioned experiment, and use machine learning algorithms to decode the cognitive states of subjects when they are looking at pictures or when they are looking at sentences. An interesting difference between many applications of machine learning, and this study is that most machine learning algorithms have the goal of achieving the maximum possible discrimination between conditions or classes. However, for fMRI studies it is important that the pattern of activity that is identified by the algorithm is a pattern associated with the cognitive state. When using non-linear classifiers, it is possible to decode features predictive of the cognitive state, where the brain does not actually respond to these features. For example, when decoding the primary visual cortex with high enough spatial resolution, it would be possible to combine simple features with a non-linear neural network to decode the presence or absence of, for example, faces. However, this information is not actually processed in that part of the brain \cite{to:2012rev}. To avoid this problem it is recommended to only use linear classifiers when decoding cognitive states from fMRI data. The classifiers that we compare in this paper are Gaussian Naive Bayesian (GNB) classifiers, Linear Support Vector (LSV) machines, and a Multivariate Gaussian (MV) classifier.
